Case for Support

### 2021-11-16 application/backgroundToTheResource.tex
Added href to online figures

\setlength{\columnsep}{1em}
\begin{wrapfigure}{R}{0.5\textwidth}
  % \includegraphics[width=0.5\columnwidth,viewport=65 50 500 800,clip]{figures/bonsai_noCaption.pdf}
    \includegraphics[width=0.48\textwidth]{figures/roadmap-bbsrc_noCaption.png}

  \caption{Bonsai development timmeline and community adoption. (A) Timeline of
    milestones and landmark package releases. (B) Example neuroscience
    experiments developed in Bonsai over the years. (C) Example Bonsai workflow
    for tracking the positioon of objects in a video. (D) Worldwide
    distribution of visitors to the bonsai-rx.org website. (E)
    Number of downloads for each Bonsai version. (F) Cumulative number of
    registered forum users, citations of the main publication, and number of
    training events, by year (bottom panels), versus release and development
    cycle (top panel), measured in commits to main repository.}
  \label{fig:bonsai}

>>>>

\setlength{\columnsep}{1em}
\begin{wrapfigure}{R}{0.5\textwidth}
    \href{http://www.gatsby.ucl.ac.uk/~rapela/bbsrc-bbr21/roadmap-bbsrc_noCaption.png}{\includegraphics[width=0.48\textwidth]{figures/roadmap-bbsrc_noCaption.png}}

  \caption{Bonsai development timmeline and community adoption. (A) Timeline of
    milestones and landmark package releases. (B) Example neuroscience
    experiments developed in Bonsai over the years. (C) Example Bonsai workflow
    for tracking the positioon of objects in a video. (D) Worldwide
    distribution of visitors to the bonsai-rx.org website. (E)
    Number of downloads for each Bonsai version. (F) Cumulative number of
    registered forum users, citations of the main publication, and number of
    training events, by year (bottom panels), versus release and development
    cycle (top panel), measured in commits to main repository. Click on the
    image to see its online version.}

  \label{fig:bonsai}

### 2021-11-16 application/detailsOfResource.tex
Added href to online figures

\begin{figure} \begin{center}
    \includegraphics[width=5in]{figures/proposed_bonsai_extensions_combined.png}
    \caption{Extensions to Bonsai. (A) we propose to integrate machine learning
    functionality into the experimental control loop by building software
    infrastructure to allow Bonsai to communicate with existing machine
    learning software written in Python, R and Matlab. (B) flow chart
    representing the BCI application that we propose to implement with the
    machine learning functionality to be added to Bonsai. (C) Bonsai graphic
    program implementing the BCI application in (B).}

>>>>

\begin{figure} \begin{center}

    \href{http://www.gatsby.ucl.ac.uk/~rapela/bbsrc-bbr21/proposed_bonsai_extensions_combined.png}{\includegraphics[width=5in]{figures/proposed_bonsai_extensions_combined.png}}

    \caption{Extensions to Bonsai. (A) we propose to integrate machine learning
    functionality into the experimental control loop by building software
    infrastructure to allow Bonsai to communicate with existing machine
    learning software written in Python, R and Matlab. (B) flow chart
    representing the BCI application that we propose to implement with the
    machine learning functionality to be added to Bonsai. (C) Bonsai graphic
    program implementing the BCI application in (B). Click on the image to see
    its online version.}
